---
title: "Final project"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is the second slide, this work contains a plot which coud be manipulated to create a lineal model in the whole data points of a scatter plot or only a few of interest.

It uses the data set mtcars ploting weight vs miles per galon. 

## Forms of input

- Slide bars: move bars left and right to adjust the axis range
- Check boxes: check and uncheck toshow or hide the axis labels
- Brush: select the points of interest to create a linear model

## Reactive output

- Line displaing the linear model of the points selected
- Slope and intercept of the model created
- Axis adjustment by according to the values inputed on the slider bars
- Show/hide axis lablels by checking/unchecking the boxes


## Data used
```{r cars, echo = TRUE}
head(mtcars)
```

## Plot displayed (example)

```{r mtcars,echo=TRUE}
plot(mtcars$wt,mtcars$mpg,xlab="Weight",ylab= 'Miles per Galon',
         cex=1.5,pch=16,bty="n",col='gray')
abline(lm(mtcars$mpg~mtcars$wt),col='red',lwd=2)
```

